\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{url}
\usepackage{amssymb,amsmath}
\usepackage[utf8]{inputenc}
\name{Jon Sims} % Your name
\address{227 Woodstock \\ Clarendon Hills, IL 60514} % Your address
\address{(239)~$\cdot$~994~$\cdot$~3049 \\ jsims@pugetsound.edu} % Your phone number and email
%Do github and website

\begin{document}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, SQL/PLSQL, Java, C/C++/C\#, Ruby, Bash, Haskell,\\(in order of experience)& HTML/CSS/Javascript, Prolog, Assembly, Common Lisp, Batch\\
Databases & Oracle Database 12c, Postgre, MySQL, SQLite\\
Other Technologies & Oracle Peopletools 8.53, Enterprise Linux Systems \\& (Debian, Fedora, Ubuntu), SVN/Git, Django, Rails, Node.js/Express, \LaTeX\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience} 

\begin{rSubsection}{University of Puget Sound}{September 2013 -- Present}{Junior Database Analyst}{Tacoma, WA}

\item I am a work study student working with the university's databases to replace their legacy database structure with the newer Oracle Database $12$c and Oracle Peopletools.
\item I designed queries and views in PL/SQL for various academic and financial departments.
\item Initially, I worked as part of the "Optimize Team", but we've now moved onto the "Maximize" phase. Same job and work, but slightly different titles. 
\item I've successfully replaced many legacy reports with Peoplesoft queries. 
\item I work under the senior developers who build the university's SQL database in the first place, thus have picked up a foundational understanding of database administration.


\end{rSubsection}


\begin{rSubsection}{University of Puget Sound}{September 2014 -- Present}{Tutor for the Computer Science department}{Tacoma, WA}
\item I also tutor for the computer science department for several hours per week, typically helping students of introductory and intermediate computer science classes.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Risk Technology Solutions}{June 2013 -- August 2013}{Junior Linux Systems Administrator}{Charlotte, NC}
\item I installed several programs onto their servers for the purpose of analyzing stock positions and portfolios. 
\item Risktech writes customized software for individual firms based on their market analysis needs. Rather than rewriting redundant code for similar problems, they want to look into an open source platform on which to write customized software. 
\item My role was to install and test the Opengamma platform for them in order to achieve an open source solution. 
\item I analyzed the potential costs and benefits of developing atop Opengamma .
\item I also began the reconstruction of a corrupted Oracle database.
\end{rSubsection}

\begin{rSubsection}{Self-employed}{December 2012 -- Present}{Freelance Web Developer}{Clarendon Hills, IL}
\item In $2012$, my uncle needed a website to show off his restaurant to the world. I wrote the website's code and set up its hosting. It existed at \url{tomsgrill.com}, but has since been deactivated as he sold the restaurant earlier this year.
\item I set up an apache$2$ webserver for my home server at the address \url{jonsims.me} .
\item In the summer of $2014$, I designed a website at \url{j-walking.biz} for another client.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\begin{rSubsection}{University of Puget Sound}{August 2013 -- June 2016}{B.S. in Computer Science \& Mathematics (double major)\\Honors program}{Tacoma, WA} 
\item I am currently a second-year student, but have third-year standing due to additional course credits from summer classes.
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	Interests
%----------------------------------------------------------------------------------------

\begin{rSection}{Interests}

\begin{rSubsection}{Association for Computing Machinery}{August 2013 -- Present}{Project Organizer}{University of Puget Sound}

\item I've participated in this club through a couple of projects since the beginning of freshman year, and have now been elected into one of its leadership positions as the project organizer. 
\item We have hosted several hackathons, including the ACM intercollegiate programming competition for the past two years. 
\item This past semester, we've begun work on several IOS/Android apps, including:
  \begin{itemize}
    \item LoggerBytes, which queries the school's database for how many dining dollars a student has left 
    \item Eventi, a method of viewing campus event posters from a mobile device
    \item Space Tower Defense, a simple tower defense game
  \end{itemize}
\item We've also constructed a pseudo-supercomputer, which can successfully run programs in parallel, out of several raspberry pi computers. 
\end{rSubsection}
\begin{rSubsection}{Additional collegiate involvement}{\ }{\ }{University of Puget Sound}
\item Certified trip leader for Puget Sound Outdoors, as well as first-aid and CPR certified
\item DJ for the college radio station KUPS for the past two semesters
\item Interfraternity Council's Director of Public Relations, elected in the fall of 2014, and will serve until the spring of 2016
\item Refounding father of a chapter of the Beta Theta Pi fraternity
\item Participant in the Putnam mathematics competition
\item Member of the honors program
\end{rSubsection}



\end{rSection}

\end{document}
