\documentclass{resume} % Use the custom resume.cls style

\usepackage[adobe-garamond]{mathdesign}
\usepackage[T1]{fontenc}
%\usepackage{garamond}
\normalfont
\usepackage[left=0.65in,top=0.8in,right=0.65in,bottom=0.725in]{geometry} % Document margins
\usepackage{url}
%\usepackage{amssymb,amsmath}
\usepackage[utf8]{inputenc}
\name{Jon Sims} 
\address{227 Woodstock, Clarendon Hills, IL 60514} 
\address{(239)~$\cdot$~994~$\cdot$~3049 \\ jsims@pugetsound.edu \\ \url{jonsims.me}}
\begin{document}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, SQL/PLSQL, Java, Ruby, C/C++/C\#, Bash, Haskell,\\(in order of experience)& HTML/CSS/Javascript, Prolog, Assembly, Common Lisp, Batch\\
Databases & Oracle Database 12c, Postgre, MySQL, SQLite\\
Other Technologies & Oracle Peopletools 8.53, Enterprise Linux Systems \\& (Debian, Fedora, Ubuntu), SVN/Git, Django, Rails, Node.js\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience} 

\begin{rSubsection}{University of Puget Sound}{September 2013 -- Present}{Junior Database Analyst}{Tacoma, WA}

\item I am a work study student working with the university's databases to replace queries and views from their legacy database structure with those of the newer Oracle Peoplesoft.
\item These views are written in PL/SQL, and queries using Oracle Peopletools for various academic and financial departments.
\item Initially, I worked as part of the "Optimize Team", but we've now moved onto the "Maximize" phase. Same job and work, but slightly dif$\mathit{}$ferent titles. 
\item I've successfully replaced many legacy reports with Peoplesoft queries. 
\item I work under the senior developers who build the university's SQL database in the first place, thus have picked up a foundational understanding of database administration.


\end{rSubsection}


\begin{rSubsection}{University of Puget Sound}{September 2014 -- Present}{Tutor for the Computer Science department}{Tacoma, WA}
\item I also tutor for the computer science department for several hours per week, typically helping students of introductory and intermediate computer science classes.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Risk Technology Solutions}{June 2013 -- August 2013}{Junior Linux Systems Administrator}{Charlotte, NC}
\item I installed several programs onto their servers for the purpose of analyzing stock positions and portfolios. 
\item Risktech writes customized software for individual firms based on their market analysis needs. Rather than rewriting redundant code for similar problems, they want to look into an open source platform on which to write customized software. 
\item My role was to install and test the Opengamma platform for them in order to achieve an open source solution. 
\item I analyzed the potential costs and benefits of developing atop Opengamma .
\item I also began the reconstruction of a corrupted Oracle database.
\end{rSubsection}

\begin{rSubsection}{Self-employed}{December 2012 -- Present}{Freelance Web Developer}{Clarendon Hills, IL}
\item In $2012$, my uncle needed a website to show off his restaurant to the world. I wrote the website's code and set up its hosting. It existed at \url{tomsgrill.com}, but has since been deactivated as he sold the restaurant earlier this year.
\item I set up an apache$2$ webserver for my home server at the address \url{jonsims.me} .
\item In the summer of $2014$, I designed a website at \url{j-walking.biz} for another client.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\begin{rSubsection}{University of Puget Sound}{August 2013 -- June 2016}{B.S. in Computer Science \& Mathematics (double major)\\Honors program}{Tacoma, WA} 
\item I am currently a second-year student, but have third-year standing due to additional course credits from summer classes.
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	Interests
%----------------------------------------------------------------------------------------

\begin{rSection}{Interests}

\begin{rSubsection}{Association for Computing Machinery}{August 2013 -- Present}{Project Organizer and President}{University of Puget Sound}

\item I've participated in this club through a couple of projects since the beginning of freshman year, and have served as its project organizer and president for the past year.
\item We have hosted several hackathons, including the ACM intercollegiate programming competition.
\item We've worked on a Rover project this past year, automating the driving of an RC car using Arduino ultrasonic sensors.
\item From last summer, we built a native IOS/Android/web app Eventi, a method of viewing campus event posters from a mobile device as well as posting event information for our campus community.
\item We've also constructed a pseudo-supercomputer, which can successfully run threaded programs in parallel, out of several raspberry pi computers. 
\end{rSubsection}

\begin{rSubsection}{KUPS 90.1FM}{August 2015 -- Present}{Communications Engineer and Webmaster}{University of Puget Sound}
\item Worked on several software projects for the station, most notibly a new radio automation system/scheduling software as an open-source project. The software datamines music information from several online sources using available information from music files (using either metadata or filenames), and can also find new, currently-trending music to add to the rotation. After parsing and processing metadata, the software queries these same sources for several metrics of popularity (enabling the software to rank the frequency with which the music should be played) as well as for genres, subgenres, and similar artists associated with the music. Finally, using these various classification features, the software generates playlists of similar music using a k-nearest-neighbors approach (randomly selecting the next track from the k neighbors, weighted by closeness).
\item Additionally, performed basic systems administration tasks on the various computer systems used within the station, as well as regular maintenance of the website [kups.net](www.kups.net).
\end{rSubsection}
\begin{rSubsection}{Additional collegiate involvement}{\ }{\ }{University of Puget Sound}
\item Certified trip leader for Puget Sound Outdoors, as well as first-aid and CPR certified.
\item Interfraternity Council's Director of Public Relations, elected in the fall of 2014 to serve for a full year.
\item DJ for KUPS for the past two years.
\item Founding father of a chapter of the Beta Theta Pi fraternity.
\item Participant in the Putnam mathematics competition.
\end{rSubsection}



\end{rSection}

\end{document}
